### 2022-01-12 manuscript/manuscript.Rmd
Update manuscript.Rmd

After Study One, but before beginning Study Two, we decided to also compute a secondary (not preregistered) PPPR prevalence estimate based on how many of randomly sampled articles were themselves examples of PPPR. To align the two estimates, we only used the first 10 eligible articles for each journal, and therefore the total number of assessed articles was 2066 as above. These two prevalence measures have complementary strengths and limitations. For the primary prevalence estimate PPPR was identified through searches of article web pages for linked PPPR. Its accuracy therefore depends on journals actively and visibly linking to PPPR on their webpages. However, it is not dependent on PPPR being indexed in Web of Science databases. By contrast, for the secondary prevalence estimate PPPR was identified by checking if sampled articles were themselves examples of PPPR. Thus, it does not rely on journals linking to relevant PPPR, but it does rely on PPPR being indexed in Web of Science databases, because that is how the sampled articles were identified.

@@

# Open practices statement
The study protocol (rationale, methods, and analysis plan) was pre-registered on February 14th, 2020 (https://osf.io/hjvnw/). All departures from this protocol are explicitly acknowledged in Supplementary Information A. All data exclusions and measures conducted during this study are reported in this manuscript. All data, materials, and analysis scripts are publicly available on the Open Science Framework (https://osf.io/8b6jy/). To facilitate reproducibility this manuscript was written by interleaving regular prose and analysis code using knitr (Xie, 2017) and papaja (Aust & Barth, 2020), and is available in a Code Ocean container (https://doi.org/10.24433/CO.1811964.v1) which re-creates the software environment in which the original analyses were performed.

>>>>

After Study One, but before beginning Study Two, we decided to also compute a secondary (not preregistered) PPPR prevalence estimate based on how many of randomly sampled articles were themselves examples of PPPR. To align the two estimates, we only used the first 10 eligible articles for each journal, and therefore the total number of assessed articles was 2066 as above. These two prevalence measures have complementary strengths and limitations. For the primary prevalence estimate PPPR was identified through searches of article web pages for linked PPPR. Its accuracy therefore depends on journals actively and visibly linking to PPPR on their webpages. However, it is not dependent on PPPR being indexed in Web of Science databases. By contrast, for the secondary prevalence estimate PPPR was identified by checking if sampled articles were themselves examples of PPPR. Thus, it does not rely on journals linking to relevant PPPR, but it does rely on PPPR being indexed in Web of Science databases, because that is how the sampled articles were identified. Note that our primary estimate was also time-restricted in the sense that any identified PPPR must have been published after 2018 (when the sampled articles were published. By contrast, our secondary estimate could theoretically detect PPPRs pertaining to any previously target articles, regardless of their publication date.

@@

# Open practices statement
The study protocol (rationale, methods, and analysis plan) was pre-registered on February 14th, 2020 (https://osf.io/hjvnw/). All departures from this protocol are explicitly acknowledged in Supplementary Information A. All data exclusions and measures conducted during this study are reported in this manuscript. All data, materials, and analysis scripts are publicly available on the Open Science Framework (https://osf.io/8b6jy/). To facilitate reproducibility this manuscript was written by interleaving regular prose and analysis code using knitr (Xie, 2017) and papaja (Aust & Barth, 2020), and is available in a Code Ocean container (https://doi.org/10.24433/CO.3805142.v1) which re-creates the software environment in which the original analyses were performed.
